### 2015-05-24 docs/report/serialization_transference.tex

Nevertheless, there are additional time consuming tasks other than the main computation that need to be considered when performing the operation in parallel in programs with no shared memory. These are:
\begin{itemize}
  \item Partitioning or joining the elements to transfer.
  \item Serializing/deserializing the elements to transfer.
  \item Transferring the elements back and forth between the main thread and the workers.
\end{itemize}

@@

Considering the definition of a \code{Transferable} the latter seems like a good alternative to minimize both \(T_{s}\) and \(T_{s}\). Even more so when one considers that otherwise objects are copied using structured cloning (explained in section \textbf{2.7.6} of that same standard).

\subsection{Benchmarks}
To verify the above we put together two benchmarks that aim to verify the difference between invoking \code{postMessage} with and without structured cloning for a \ttarray{}. Both transfer a \ttarray{} back and forth between the UI thread and a worker; the only difference between the two is that one has 100,000 (a hundred thousand) elements in the \ttarray{} and the other one 1,000,000 (a million).

\subsubsection{With 100,000 elements}
The following is the code for the benchmark:
\bmcode{http://jsperf.com/transferrable-vs-cloning}{../../spikes/1.2/transferrableVsCloning.js}

@@

\subsubsection{With 1,000,000 elements}
The following is the code for the benchmark:
\bmcode{http://jsperf.com/longer-transferrable-vs-cloning}{../../spikes/1.2/longerTransferrableVsCloning.js}

@@

@@

For that reason we will only work with {\ttarray{}}s and all of them will be passed to/from Web Workers by transferring their ownership.

>>>>

Nevertheless, there are additional time consuming tasks other than the main computation that need to be considered when performing the operation in parallel in programs where memory is not shared by default. These are:
\begin{itemize}
  \item Partitioning or joining the elements to transfer.
  \item Serializing/deserializing the elements to transfer.
  \item Transferring the elements back and forth between the main thread and the workers.
\end{itemize}

@@

Considering the definition of a \code{Transferable} the latter seems like a good alternative to minimize both \(T_{s}\) and \(T_{t}\). Even more so when one considers that otherwise objects are copied using structured cloning (explained in section \textbf{2.7.6} of that same standard).

In the case of \tsabuffer{} instances, \(T_{p}\) is also minimized. Instead of actually making copies of the buffer's data, all that is required a simple calculation to determine the boundaries on which each Web Worker should operate. Additionally, \(T_{t}\) should also decrease as there is no need to transfer the \tsabuffer{} back to the UI thread.

\subsection{Benchmarks}
To verify the above we put together two benchmarks that aim to verify the difference between invoking \code{postMessage} with and without structured cloning for a \ttarray{}. Since \tsabuffer{}s cannot be cloned, we created a separate benchmark to compare the performance of transferring \tsabuffer{}s and \tabuffer{}s.

The benchmarks transfer the arrays back and forth between the UI thread and a worker; the only difference between the two is that one has 100,000 (a hundred thousand) elements in the array and the other one 1,000,000 (a million).

\subsubsection{TypedArray With 100,000 elements}
The following is the code for the benchmark:
\bmcode{http://jsperf.com/transferrable-vs-cloning}{../../spikes/1.2/transferrableVsCloning.js}

@@

\subsubsection{TypedArray With 1,000,000 elements}
The following is the code for the benchmark:
\bmcode{http://jsperf.com/longer-transferrable-vs-cloning}{../../spikes/1.2/longerTransferrableVsCloning.js}

@@

\subsubsection{Transferring SharedArrayBuffers and ArrayBuffers}
The following is the code for the benchmark:
\bmcode{http://jsperf.com/transfer-shared-vs-not-shared}{../../spikes/1.2/transferableSharedVsNotShared.js}

The results for it are displayed in Figure~\ref{fig:sab-vs-ab-transfer}.
\img{Transferring SharedArrayBuffers and ArrayBuffers}{../../spikes/1.2/transferableSharedVsNotShared}{fig:sab-vs-ab-transfer}

@@

For that reason we will only work with \ttarray{}s and \tstarray{}s and all of them will be passed to/from Web Workers by transferring their ownership.

Although it does not affect our decision, it is also interesting to note the big difference between transferring \tsabuffer{}s and \tabuffer{} in Firefox Nightly. This difference is probably going to be smaller over the course of time.
